Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-05-05 paper/manuscript.Rmd
Change title?

---
title: "Community context determines competition/facilitation trade-offs in pollination systems"
author: 
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
  - "Hugo J. Marrero^2^ ([hugomarrero@gmail.com](hugomarrero@gmail.com))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
# classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
---

@@

Our second objective was to investigate the relative contribution of different factors---that describe the plants' competition for pollination niches---to the pollination service. 
Generally speaking,
<!-- in the context of competition for pollination, -->
we expect that any factor that increases the amount of conspecific pollen deposited in stigmas, both in quantity and purity relative to heterospecific pollen, also has a positive effect on the pollination service.
<!-- DBS: There is no use to calling it something succinct like purity if we always have to say "purity relative to heterospecific pollen"...  -->
Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines
the share of pollen that a plant species is able to place on each of their floral visitors
<!-- DBS: The line above is very confusing and took me about five reads before I understood what you wanted to say. We need to revise it. -->
and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010]. 
See *Data Analysis* section below for more details on these four variables. 
<!-- Here, we define visit effectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*. -->

>>>>

---
title: "Community context determines competition vs. facilitation trade-offs in pollination systems"
author: 
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
  - "Hugo J. Marrero^2^ ([hugomarrero@gmail.com](hugomarrero@gmail.com))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
# classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
---

@@

Our second objective was to investigate the relative contribution of different mechanisms of pollinator mediated competition. 
Generally speaking,
<!-- in the context of competition for pollination, -->
we expect that any factor that increases the amount of conspecific pollen deposited in stigmas, both in quantity and purity relative to heterospecific pollen, also has a positive effect on the pollination service.
<!-- DBS: There is no use to calling it something succinct like purity if we always have to say "purity relative to heterospecific pollen"...  -->
Specifically, we investigated the effect of (*i*) a plant's number of shared pollinator species, (*ii*) a plant's abundance relative to the rest of the community, (*iii*) the mean visit effectiveness---a metric that combines
the share of pollen that a plant species is able to place on each of their floral visitors
<!-- DBS: The line above is very confusing and took me about five reads before I understood what you wanted to say. We need to revise it. -->
and the number of visits it receives from them, and (*iv*) the plant's functional originality [@laliberte_distance-based_2010]. 
See *Data Analysis* section below for more details on these four variables. 
<!-- Here, we define visit effectiveness of the pollinator species *i* to plant species *j* as the proportion between the visits of *i* to *j* and all visits of *i*, multiplied by the proportion between the number of pollen grains of *j* attached to individuals of *i* and all pollen attached to individuals of *i*. -->
